\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}

### 2023-04-24 Latex/paper-resum.tex
# fix some bugs in .tex file

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \biggl(G(t_0,t_2)  - G(t_0,t_1) \biggr) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0)
\end{equation}
with 
\begin{equation*}
\beta(u,t_0,x,y) = \exp\left(-\int_{u}^{t_0}k(w) dw \right) \eta(u,x,y).
\end{equation*}
The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1,x,y)}{P_{E}(t_0,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

@@

\begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}, and
\begin{equation}
M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}.
\end{equation}
Then, we have the temporal convexity adjustment for a CMS rate is approximated by
\begin{align} \label{cms_first_order_convexity}
CA(t_p) &\approx  \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \\
&\cdot  \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds + E(t_a)\nonumber 
\end{align}
with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_w dw\right)\eta(u,x,y)$ and the error $E(t_a)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{P_{E}(t_0,t_1,x,y)}{P_{E}(t_0,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_a)$ when $t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty$ when $t_a \to \infty$.
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_CMS}.
\end{proof}

>>>>

\begin{theorem}\label{Th_CA_futures}[Convexity Adjustment approximation for Futures]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for futures is 
\begin{equation}\label{ca_approximation_futures}
CA(t,t_0,t_1) = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \biggl(G(t_0,t_2)  - G(t_0,t_1) \biggr) \int_{0}^{t_0} \beta(s,t_0,\bar{x}_0(t_0),\bar{y}_s) \nu(s,t_2) ds + E(t_0)
\end{equation}
with 
\begin{equation*}
\beta(u,t_0,x,y) = \exp\left(-\int_{u}^{t_0}k(w) dw \right) \eta(u,x,y).
\end{equation*}
The error $E(t_0)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{\frac{P_{ois}(t_0,t_1,x,y)}{P_{ois}(t_0,t_2,x,y)} -1}{\delta_{t_0,t_1}}$ and behaves as $\mathcal{O}(t_0)$ when $t_0 \to 0$ and $\|E(t_0)\|^{2}_{2} < \infty$ when $t_0 \to \infty$. 
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_futures}.
\end{proof}

@@

\begin{theorem}\label{Th_CA_CMS}[Convexity Adjustment approximation for CMS]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}, and
\begin{equation}
M(t,t_p)= \frac{P_{ois}(t,t_p)}{01(t,t_a,t_p)}.
\end{equation}
Then, we have the temporal convexity adjustment for a CMS rate is approximated by
\begin{align} \label{cms_first_order_convexity}
CA(t_p) &\approx  \frac{\partial_x S_{a,b}(t_a,\bar{x}_0(t_a), \bar{y}_0) \partial_x M(t_a,t_p,\bar{x}_0(t_a), \bar{y}_0)}{M(0,t_p)} \int_{0}^{t_a}  \beta^2(s,t_a,\bar{x}_0(t_a),\bar{y}_s) \\
&\cdot  \exp\left(-2\int_{s}^{t_a}\partial_x (\beta(u,t_a,\bar{x}_u,\bar{y}_u) \mu(u,\bar{x}_u, \bar{y}_u,t_a,t_b))|_{\bar{x}_u=\bar{x}_{0}(t_a)}  du \right)ds + E(t_a)\nonumber 
\end{align}
with  $\beta(u,t_a,x,y) = \exp\left(-\int_{u}^{t_a}k_w dw\right)\eta(u,x,y)$ and the error $E(t_a)$ is given by (\ref{f_x_y}) with $f(x,y)=M(t_a,t_p,x,y)S_{a,b}(t_a,x,y)$ and behaves as $\mathcal{O}(t_a)$ when $t_a \to 0$ and $\|E(t_a)\|^{2}_{2} < \infty$ when $t_a \to \infty$.
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_CMS}.
\end{proof}
